Microxanox: an R package for simulating an aquatic $MICR$obial ecosystem that can occupy $OX$ic or $ANOX$ic states.

### 2022-06-08 inst/manuscript/manuscript_microxanox.Rmd

---
title: "Microxanox: an R package for simulating an aquatic $MICR$obial ecosystem that can occupy $OX$ic or $ANOX$ic states."
author:
- name: Rainer M Krug
  email: Rainer.Krug@uzh.ch;  Rainer@krugs.de
  affiliation: University of Zürich
  footnote: Corresponding Author
- name: Owen L. Petchey
  email: Owen.Petchey@ieu.uzh.ch
  affiliation: University of Zürich
address:
- code: University of Zürich
  address: Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse
    190, 8057 Zurich
footnote:
  - code: 1
    text: "Corresponding Author"
  - code: 2
    text: "Equal contribution"
keywords: reproducibility; regime shift; 
abstract: |
  Ca. 100 words.
journal: "SoftwareX"
date: "`r Sys.Date()`"

@@

# \textcolor{red}{TODO}
- **\textcolor{red}{update links}**
- [x] ~~**\textcolor{red}{update cross references}**~~
- **\textcolor{red}{check keywords}**
- [x] ~~**\textcolor{red}{add more references}**~~
- **\textcolor{red}{expand on Impact and Conclusion section}**
\pagebreak

@@

| **Nr.** | **Code metadata description**                                | **Please fill in this column**                                                 |  
| :-----: | :----------------------------------------------------------- | :----------------------------------------------------------------------------- |  
|   C1    | Current code version                                         | v0.9.0                                                                         |  
|   C2    | Permanent link to code/repository used for this code version | [https://github.com/UZH-PEG/microxanox](https://github.com/UZH-PEG/microxanox) |  
|   C3    | Code Ocean compute capsule                                   |                                                                                |  
|   C4    | Legal Code License                                           | CC BY 4.0                                                                      |  
|   C5    | Code versioning system used                                  | git                                                                            |  
|   C6    | Software code languages, tools, and services used            | [R](https://cran.r-project.org/index.html)                                     |  
|   C7    | Compilation requirements, operating environments             | [R (>= 4.1.0)](https://cran.r-project.org/index.html)                          |  
|         |                                                              | magrittr                                                                       |  
|         |                                                              | tibble                                                                         |  
|         |                                                              | ggplot2                                                                        |  
|         |                                                              | patchwork                                                                      |  
|         |                                                              | grDevices                                                                      |  
|         |                                                              | stats                                                                          |  
|         |                                                              | mgcv                                                                           |  
|         |                                                              | deSolve                                                                        |  
|         |                                                              | dplyr                                                                          |  
|         |                                                              | tidyr                                                                          |  
|         |                                                              | stringr                                                                        |  
|         |                                                              | multidplyr                                                                     |  
|         |                                                              |                                                                                |  
|         |                                                              |                                                                                |  
|         |                                                              |                                                                                |  
|         |                                                              |                                                                                |  
|         |                                                              |                                                                                |  
|   C8    | If available Link to developer documentation/manual          | \textcolor{red}{TO BE ADDED}                                                   |  
|   C9    | Support email for questions                                  | Rainer.Krug@uzh.ch; Rainer@krugs.de                                            |

>>>>

---
title: "Microxanox: an R package for simulating an aquatic $MICR$obial ecosystem that can occupy $OX$ic or $ANOX$ic states."
author:
- name: Rainer M Krug
  email: Rainer.Krug@uzh.ch;  Rainer@krugs.de
  affiliation: University of Zürich
  footnote: Corresponding Author
- name: Owen L. Petchey
  email: Owen.Petchey@ieu.uzh.ch
  affiliation: University of Zürich
address:
- code: University of Zürich
  address: Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse
    190, 8057 Zurich
footnote:
  - code: 1
    text: "Corresponding Author"
  - code: 2
    text: "Equal contribution"
keywords: 
  - reproducibility
  - regime shift 
  - stable state
  - ordinary differential equations
abstract: |
  $Microxanox$ is an R package to simulate a three functional group system (cyanobacteria, phototrophic sulfur bacteria, and sulfate-reducing bacteria) with four chemical substrates (phosphorus, oxygen, reduced sulfur, and oxidized sulfur) osing a set of ordinary differential equations. Simulations can be run individually or over a parameter range, to find stable states.  The model features multiple species per functional group, where the number is only limited by computational constraints.
  The R package is constructed in such a way, that the results contain the input parameter used, so that a saved results can be loaded again and the simulation be repeated.
journal: "SoftwareX"
date: "`r Sys.Date()`"

@@

# \textcolor{red}{TODO}
- **\textcolor{red}{update links}**
- [x] ~~**\textcolor{green}{update cross references}**~~
- [x] ~~**\textcolor{green}{add abstract}**~~
- [x] ~~**\textcolor{green}{check keywords}**~~
- [x] ~~**\textcolor{green}{add more references}**~~
- [x] ~~**\textcolor{green}{expand on Impact section}**~~
- [x] ~~**\textcolor{green}{expand on Conclusion section}**~~
\pagebreak

@@

| **Nr.** | **Code metadata description**                                | **Please fill in this column**                                                 |  
| :-----: | :----------------------------------------------------------- | :----------------------------------------------------------------------------- |  
|   C1    | Current code version                                         | v0.9.0                                                                         |  
|   C2    | Permanent link to code/repository used for this code version | [https://github.com/UZH-PEG/microxanox](https://github.com/UZH-PEG/microxanox) |  
|   C3    | Code Ocean compute capsule                                   |                                                                                |  
|   C4    | Legal Code License                                           | CC BY 4.0                                                                      |  
|   C5    | Code versioning system used                                  | git                                                                            |  
|   C6    | Software code languages, tools, and services used            | [R](https://cran.r-project.org/index.html)                                     |  
|   C7    | Compilation requirements, operating environments             | [R (>= 4.1.0)](https://cran.r-project.org/index.html)                          |  
|         |                                                              | magrittr                                                                       |  
|         |                                                              | tibble                                                                         |  
|         |                                                              | ggplot2                                                                        |  
|         |                                                              | patchwork                                                                      |  
|         |                                                              | grDevices                                                                      |  
|         |                                                              | stats                                                                          |  
|         |                                                              | mgcv                                                                           |  
|         |                                                              | deSolve                                                                        |  
|         |                                                              | dplyr                                                                          |  
|         |                                                              | tidyr                                                                          |  
|         |                                                              | stringr                                                                        |  
|         |                                                              | multidplyr                                                                     |  
|   C8    | If available Link to developer documentation/manual          | \textcolor{red}{TO BE ADDED}                                                   |  
|   C9    | Support email for questions                                  | Rainer.Krug@uzh.ch; Rainer@krugs.de                                            |
